Mergeable Types

### 2017-02-27 paper/evaluation.tex
edits

More importantly, the cost of computation grows sub-linearly. This is because
of efficient merge function on ropes~\ref{ropes} enabled by Irmin's
content-addressed storage backend, and more expensive operational
transformation of merging concurrent edits to leaf nodes~\ref{lists} is invoked
rarely on small. On average, we measured that at a distance of 256, for merging
the two documents with 1743 characters, 50 list merges were performed on
strings of average length 13. A purely list based approach would require the
polynomial time edit sequence algorithm to be applied on the entire document
twice. Compare to this, the rope implementation has much better algorithmic
complexity. We measured that by representing the entire document using
mergeable list type, in addition to slowing down each edit operation, the merge
at a distance of 256 was 2.3 times slower than the rope implementation.

>>>>

More importantly, the cost of computation grows sub-linearly. This is because
of efficient merge function on ropes~\ref{sec:ropes} enabled by Irmin's
content-addressed storage backend, and more expensive operational
transformation of merging concurrent edits to leaf nodes~\ref{sec:lists} is invoked
rarely on small. On average, we measured that at a distance of 256, for merging
the two documents with 1743 characters, 50 list merges were performed on
strings of average length 13. A purely list based approach would require the
polynomial time edit sequence algorithm to be applied on the entire document
twice. Compare to this, the rope implementation has much better algorithmic
complexity. We measured that by representing the entire document using
mergeable list type, in addition to slowing down each edit operation, the merge
at a distance of 256 was 2.3 times slower than the rope implementation.
